### 2024-02-05 docs/projects/noj/ggplot.qmd
Noj - rerendered

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ggplot_files/md-default0.js" type="text/javascript"></script><script src="ggplot_files/md-default1.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

# Exploring ggplot

::: {.sourceClojure}
```clojure
(ns ggplot
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]))
```
:::

@@

@@

<g id="surface6">

@@

@@

Trying to mimic [cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list (WIP):

::: {.sourceClojure}
```clojure
(let [f (-> plot
            (r$ 'facet)
            (r$ 'params)
            (r$ 'facets))]
  (when (-> `(is.null ~f)
            r
            r->clj)
    (let [facet (-> `(ls ~f)
                    r
                    (r->clj)
                    first)]
      {:facet facet
       :facet-levels (-> plot
                         (r$ 'data)
                         (r/bra facet))})))
```
:::

::: {.printedClojure}
```clojure
{:facet "cyl", :facet-levels # A tibble: 234 × 1
     cyl
   &lt;int&gt;
 1     4
 2     4
 3     4
 4     4
 5     6
 6     6
 7     6
 8     4
 9     4
10     4
# ℹ 224 more rows
}

@@

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>

>>>>

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ggplot_files/md-default5.js" type="text/javascript"></script><script src="ggplot_files/md-default6.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

# Exploring ggplot
following
[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list
in representing a plot as a data structure.

::: {.sourceClojure}
```clojure
(ns ggplot
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.walk :as walk]
            [tablecloth.api :as tc]))
```
:::

@@

```{=html}

@@

<g id="surface428">

@@

```

@@

::: {.sourceClojure}
```clojure
(defn gg-facet [ggplot]
  (let [f (-> ggplot
              (r$ 'facet)
              (r$ 'params)
              (r$ 'facets))]
    (when (-> `(is.null ~f)
              r
              r->clj)
      (let [facet (r `(ls ~f))]
        {:facet facet
         :facet-levels (-> plot
                           (r$ 'data)
                           (r/bra facet))}))))
```
:::

::: {.sourceClojure}
```clojure
(-> plot
    gg-facet
    (update-vals r->clj))
```
:::

```{=html}
<div><p>{</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet ["cyl"]</code></pre></div><table><tr><td valign="top"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet-levels
</code></pre></div></td><td><div style="margin-left:10px;"><span data-qmd="_unnamed [234 1]:

| :cyl |
|-----:|
|    4 |
|    4 |
|    4 |
|    4 |
|    6 |
|    6 |
|    6 |
|    4 |
|    4 |
|    4 |
|  ... |
|    4 |
|    4 |
|    5 |
|    5 |
|    4 |
|    4 |
|    4 |
|    4 |
|    6 |
|    6 |
|    6 |

"></span></div></td></tr></table></div><p>}</p></div>
```

::: {.sourceClojure}
```clojure
(r/require-r '[base])
```
:::

::: {.printedClojure}
```clojure
nil

@@

::: {.sourceClojure}
```clojure
(defn ggolot->clj
  ([r-obj
    options]
   (ggolot->clj r-obj options []))
  ([r-obj
    {:as options
     :keys [avoid]}
    path]
   #_(prn path)
   (let [relevant-names (some->> r-obj
                                 r.base/names
                                 r->clj
                                 (filter (complement avoid)))]
     (cond
       ;;
       ;; a named list or a ggproto object
       (seq relevant-names) (->> relevant-names
                                 (map (fn [nam]
                                        [(keyword nam) (-> r-obj
                                                           (r$ nam)
                                                           (ggolot->clj options
                                                                        (conj path nam)))]))
                                 (into {}))
       ;;
       ;; a ggproto method
       (-> r-obj
           r.base/class
           r->clj
           first
           (= "ggproto_method"))
       :ggproto-method
       ;;
       ;; an unnamed list
       (-> r-obj
           r.base/is-list
           r->clj
           first)
       (-> r-obj
           r.base/length
           r->clj
           first
           range
           (->> (mapv (fn [i]
                        (prn [path (inc i)])
                        (-> r-obj
                            (r/brabra (inc i))
                            (ggolot->clj options
                                         (conj path [i])))))))
       ;;
       (r.base/is-atomic r-obj) (try (r->clj r-obj)
                                     (catch Exception e
                                       (-> r-obj println with-out-str)))
       :else r-obj))))
```
:::

::: {.sourceClojure}
```clojure
(-> "(ggplot(mpg, aes(cty, hwy))
         + geom_point())"
    r
    (ggolot->clj {:avoid #{"data" "plot_env"}}))
```
:::

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"]}}

::: {.sourceClojure}
```clojure
(defn h4 [title]
  (kind/hiccup [:h3 title]))
```
:::

::: {.sourceClojure}
```clojure
(defn ggplot-summary [r-code]
  (let [plot (r r-code)
        clj (-> plot
                (ggolot->clj {:avoid #{"data" "plot_env"}})
                (->> (walk/postwalk (fn [form]
                                      (if (and (symbol? form)
                                               (-> form str (= "~")))
                                        (str form)
                                        form)))))]
    (kind/fragment
     [(h4 "code")
      (kind/md
       (format "\n```{r eval=FALSE}\n%s\n```\n"
               r-code))
      (h4 "image")
      (plotting/plot->buffered-image plot)
      (h4 "clj")
      (kind/pprint clj)])))
```
:::

::: {.sourceClojure}
```clojure
(ggplot-summary
 "(ggplot(mpg, aes(cty, hwy))
         + geom_point())")
```
:::

```{=html}
<h3>code</h3>
```

```{r eval=FALSE}
(ggplot(mpg, aes(cty, hwy))
         + geom_point())
```

```{=html}
<h3>image</h3>
```

```{=html}
<img src="ggplot_files/0.png" style="width:100%;" />
```

```{=html}
<h3>clj</h3>
```

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x ["~" cty], :y ["~" hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"]}}

## Exlploring a few plots

### A scatterplot

::: {.sourceClojure}
```clojure
(ggplot-summary
 "(ggplot(mpg, aes(cty, hwy))
         + geom_point())")
```
:::

```{=html}
<h3>code</h3>
```

```{r eval=FALSE}
(ggplot(mpg, aes(cty, hwy))
         + geom_point())
```

```{=html}
<h3>image</h3>
```

```{=html}
<img src="ggplot_files/1.png" style="width:100%;" />
```

```{=html}
<h3>clj</h3>
```

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x ["~" cty], :y ["~" hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"]}}

### A scatterplot with colours

::: {.sourceClojure}
```clojure
(ggplot-summary
 "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point())")
```
:::

```{=html}
<h3>code</h3>
```

```{r eval=FALSE}
(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point())
```

```{=html}
<h3>image</h3>
```

```{=html}
<img src="ggplot_files/2.png" style="width:100%;" />
```

```{=html}
<h3>clj</h3>
```

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

### A scatterplot with colours and smoothing

::: {.sourceClojure}
```clojure
(ggplot-summary
 "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method=\"lm\"))")
```
:::

```{=html}
<h3>code</h3>
```

```{r eval=FALSE}
(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method="lm"))
```

```{=html}
<h3>image</h3>
```

```{=html}
<img src="ggplot_files/3.png" style="width:100%;" />
```

```{=html}
<h3>clj</h3>
```

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
  {:aes_params [],
   :stat
   {:extra_params ["na.rm" "orientation"],
    :super :ggproto-method,
    :compute_group :ggproto-method,
    :required_aes ["x" "y"],
    :setup_params :ggproto-method,
    :dropped_aes ["weight"]},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
   :geom
   {:setup_params :ggproto-method,
    :super :ggproto-method,
    :draw_key :ggproto-method,
    :extra_params ["na.rm" "orientation"],
    :required_aes ["x" "y"],
    :draw_group :ggproto-method,
    :optional_aes ["ymin" "ymax"],
    :rename_size [true],
    :setup_data :ggproto-method,
    :default_aes
    {:colour ["#3366FF"],
     :fill ["grey60"],
     :linewidth [1.0],
     :linetype [1.0],
     :weight [1.0],
     :alpha [0.4]}},
   :stat_params
   {:na.rm [false],
    :method ["lm"],
    :n [80.0],
    :orientation [nil],
    :level [0.95],
    :fullrange [false],
    :se [true],
    :formula nil,
    :method.args [],
    :span [0.75]},
   :constructor {: nil, :method ["lm"]},
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

### A scatterplot with colours, smoothing, and facets

::: {.sourceClojure}
```clojure
(ggplot-summary
 "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method=\"lm\")
         + facet_wrap(~cyl))")
```
:::

```{=html}
<h3>code</h3>
```

```{r eval=FALSE}
(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method="lm")
         + facet_wrap(~cyl))
```

```{=html}
<h3>image</h3>
```

```{=html}
<img src="ggplot_files/4.png" style="width:100%;" />
```

```{=html}
<h3>clj</h3>
```

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position {:compute_layer :ggproto-method, :super :ggproto-method}}
  {:aes_params [],
   :stat
   {:extra_params ["na.rm" "orientation"],
    :super :ggproto-method,
    :compute_group :ggproto-method,
    :required_aes ["x" "y"],
    :setup_params :ggproto-method,
    :dropped_aes ["weight"]},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
   :geom
   {:setup_params :ggproto-method,
    :super :ggproto-method,
    :draw_key :ggproto-method,
    :extra_params ["na.rm" "orientation"],
    :required_aes ["x" "y"],
    :draw_group :ggproto-method,
    :optional_aes ["ymin" "ymax"],
    :rename_size [true],
    :setup_data :ggproto-method,
    :default_aes
    {:colour ["#3366FF"],
     :fill ["grey60"],
     :linewidth [1.0],
     :linetype [1.0],
     :weight [1.0],
     :alpha [0.4]}},
   :stat_params
   {:na.rm [false],
    :method ["lm"],
    :n [80.0],
    :orientation [nil],
    :level [0.95],
    :fullrange [false],
    :se [true],
    :formula nil,
    :method.args [],
    :span [0.75]},
   :constructor {: nil, :method ["lm"]},
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x ["~" cty], :y ["~" hwy], :colour ["~" [factor cyl]]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet
 {:params
  {:dir ["h"],
   :nrow nil,
   :as.table [true],
   :free {:x [false], :y [false]},
   :drop [true],
   :strip.position ["top"],
   :ncol nil,
   :facets {:cyl ["~" cyl]},
   :labeller
   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55eafa698ac0&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
  :shrink [true],
  :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>
```

### 2024-02-05 docs/projects/noj/index.qmd
Noj - rerendered

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default0.js" type="text/javascript"></script><script src="index_files/md-default1.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

@@

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/index.clj">projects/noj/notebooks/index.clj</a></small></small></pre></div>

>>>>

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default0.js" type="text/javascript"></script><script src="index_files/md-default1.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

@@

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/index.clj">projects/noj/notebooks/index.clj</a></small></small></pre></div>
```

### 2024-02-05 docs/projects/noj/ml.qmd
Noj - rerendered

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ml_files/md-default0.js" type="text/javascript"></script><script src="ml_files/md-default1.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

@@

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8908     -0.2103      0.0371      0.2256      0.8160

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.0708     0.3356     6.1706     0.0000 ***
sepal-width         0.5954     0.0889     6.6968     0.0000 ***
petal-length        0.6671     0.0715     9.3273     0.0000 ***
petal-width        -0.4532     0.1618    -2.8002     0.0062 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3363 on 96 degrees of freedom
Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37

@@

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ml.clj">projects/noj/notebooks/ml.clj</a></small></small></pre></div>

>>>>

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ml_files/md-default0.js" type="text/javascript"></script><script src="ml_files/md-default1.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

@@

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7904     -0.2163      0.0132      0.1774      0.8282

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.1092     0.2799     7.5344     0.0000 ***
sepal-width         0.5826     0.0743     7.8394     0.0000 ***
petal-length        0.7037     0.0624    11.2696     0.0000 ***
petal-width        -0.5557     0.1425    -3.8986     0.0002 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3015 on 96 degrees of freedom
Multiple R-squared: 0.8707,    Adjusted R-squared: 0.8667
F-statistic: 215.5039 on 4 and 96 DF,  p-value: 1.668e-42

@@

```{=html}
<div style="background-color:grey;height:2px;width:100%;"></div>
```

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ml.clj">projects/noj/notebooks/ml.clj</a></small></small></pre></div>
```
